---
title: "Developing Data Products Course Project Presentation"
author: "Metehan Soysal"
date: "2023-04-01"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
```

## Introduction

- This presentation provides an overview for the Developing Data Products Course Project.

- The web application can be found at the link here: [Project Website](https://msoysal.shinyapps.io/Final_Project/).

- The source code for the project can be found here: [Source Code](https://github.com/marino35/Developing-Data-Products-Course-Project/tree/master)

## Overview
- This project is using the [Customers dataset](https://www.kaggle.com/datasets/datascientistanna/customers-dataset) from Kaggle to predict a Spending Score based on demographics data.

- Application uses the dataset to train a model using RandomForest and predict a score based on user inputted values.

- It also provides a plot that shows the relationship of Age vs. Spending Score by Gender once the user inputted values.

## Customer Dataset
- This data is a detailed analysis of a imaginative shop's ideal customers. 
- It helps a business to better understand its customers. 
- The owner of a shop gets information about Customers through membership cards.
- Dataset consists of 2000 records and 8 columns
```{r echo = FALSE, comment=""}
cust_data <- read.csv("Customers.csv")
#head(cust_data)
str(cust_data)
```

## Prediction Model and the R Code
- This application was built by using a shiny app with ui.R and server.R files. It is hosted in shinyapps.io website.

- Prediction model is built by using RandomForest as seen below:

```{r echo = TRUE, fontsize = 4}
predict_score <- function(input1, input2, input3, input4, input5, input6) 
                {
                model <- randomForest(Spending.Score..1.100. ~ ., data = cust_data)
                # Prepare input data for score
                new_data <- data.frame(Gender = input1, Age = input2, 
                        Annual.Income.... = input3, Profession = input4, 
                        Work.Experience = input5, Family.Size = input6)
                
                # Make prediction and return result
                prediction <- predict(model, new_data)
                return(prediction)}
```

